Effective multi-body SU($N$)-symmetric interactions of ultracold fermionic atoms on a 3-D lattice

### 2019-02-27 multi_body_interactions/papers/theory/reviews_NJP/final_reviews/referee_response_2.tex

\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\green}[1]{\textcolor{green}{#1}}

\begin{document}

\section*{Referee 2}

We thank the referee for taking the time to read and reconsider our
revised manuscript.  Concerning the comments:

\blue{I read the replies from the authors and other report and
  recommend the publication.}

\blue{There are a few discussions on ``renormalization'' schemes in
  the article and in Referee 1's report.  Let me comment on the scheme
  in the manuscript. The scheme used here (more precisely
  ``regularization'' scheme) is a quite standard and has been commonly
  used in many-body studies since the beginning of many-body
  diagrammatic calculations. It is based on a k-space ``pseudo''
  potential.  From the point of view of low energy few-body physics
  studied here, it is indeed equivalent to the other well known
  standard real space ``differential pseudo'' potential Referee A
  might have in mind (I speculate that what he/she meant by ``pseudo
  potential''). But more importantly, it can be easily and
  straightforwardly generalized to arbitrary dimensions and can be
  integrated into studies of complex/sophisticated collective
  many-body effects associated with Fermi surfaces and/or sound waves
  in symmetry breaking states.}

We thank the referee for their recommendation to publish our
manuscript, and for their input to help clarify a point of confusion
in our exchanges with referee 1.  While our original response to
referee 1 was imprecise in conflating the term ``renormalization
scheme'' with ``regularization scheme'', we have gone through to make
sure that our manuscript uses these terms properly.

### 2019-03-03 multi_body_interactions/papers/theory/reviews_NJP/final_reviews/referee_response_2.tex

We thank the referee for taking the time to read and reconsider our
revised manuscript.  Concerning the comments:

\blue{I read the replies from the authors and other report and
  recommend the publication.}

\blue{There are a few discussions on ``renormalization'' schemes in
  the article and in Referee 1's report.  Let me comment on the scheme
  in the manuscript. The scheme used here (more precisely
  ``regularization'' scheme) is a quite standard and has been commonly
  used in many-body studies since the beginning of many-body
  diagrammatic calculations. It is based on a k-space ``pseudo''
  potential.  From the point of view of low energy few-body physics
  studied here, it is indeed equivalent to the other well known
  standard real space ``differential pseudo'' potential Referee A
  might have in mind (I speculate that what he/she meant by ``pseudo
  potential''). But more importantly, it can be easily and
  straightforwardly generalized to arbitrary dimensions and can be
  integrated into studies of complex/sophisticated collective
  many-body effects associated with Fermi surfaces and/or sound waves
  in symmetry breaking states.}

We thank the referee for their recommendation to publish our
manuscript, and for their input on the regularization scheme in our
manuscript.  In particular, we thank the referee for pointing out that
our approach to regularizing the two-body delta-function interaction
is a standard technique in many-body studies, equivalent to another
common technique based on a regularized real-space ``differential
pseudo-potential''.

### 2019-03-03 multi_body_interactions/papers/theory/paper.tex
some changes to latest renormalization derivation
final changes to multi-body paper for 2nd round of review

At second order in the coupling constants, the expansion for
$H_{\t{int}}^{(2)}$ in \eqref{eq:H_int_1_2} gives rise to effective
three-body interactions.  The virtual state of three-body terms in
$H_{\t{int}}^{(2)}$ cannot have two atoms in excited motional states,
as otherwise the second application of $H_{\t{int}}$ in
$H_{\t{int}}^{(2)}$ would have to address both of theses atoms to
bring them back down to the ground state, resulting in a two-body
process as in the second diagram of \eqref{eq:H_2_expansion}.  All
second-order three-body terms must therefore have only one excited
atom in the virtual state, and take the form
\begin{align}
  \begin{tikzpicture}
    \begin{feynman}
      \vertex (v1);
      \vertex[above left = of v1] (f1) {$\mu r$};
      \vertex[below left = of v1] (f2) {$\nu s$};
      \vertex[right = of v1] (vm);
      \vertex[right = of vm] (v2);
      \vertex[above = of vm] (f3) {$\mu r'$};
      \vertex[below = of vm] (f4) {$\rho t$};
      \vertex[below right = of v2] (f5) {$\rho t'$};
      \vertex[above right = of v2] (f6) {$\nu s''$};
      \diagram* {
        (f1) -- (v1) -- (f3),
        (f2) -- (v1) --  [scalar, edge label=$n\nu s'$] (v2),
        (f4) -- (v2) -- (f5),
        (v2) -- (f6), };
    \end{feynman}
  \end{tikzpicture}
  \propto K_n^2 G^{rs}_{r's'} G^{s't}_{s''t'}
  \c_{\mu r'}^\dag \c_{\nu s''}^\dag \c_{\rho t'}^\dag
  \c_{\rho t} \c_{\nu s} \c_{\mu r}
  \label{eq:H_3_2_diagram}.
\end{align}
Unlike for the two-body diagram in \eqref{eq:H_2}, the explicit
factors of $1/2$ which appear in the bare two-body Hamiltonian
$H_{\t{int}}$ in \eqref{eq:H_int} are now cancelled out by symmetry
factors which account for duplicate diagrams; this cancellation will
generally occur for all connected $M$-body diagrams with $M>2$ (see
Appendix \ref{sec:diagrams}).  The net effective three-body
interaction Hamiltonian at second order is then given by the sum over
all diagrams of the form in \eqref{eq:H_3_2_diagram}, i.e.
\begin{align}
  H_3^{(2)} = - \shrink{
    \begin{tikzpicture}
      \begin{feynman}
        \vertex (v1);
        \vertex[above left = of v1] (f1);
        \vertex[below left = of v1] (f2);
        \vertex[right = 4em of v1] (v2);
        \vertex[above right = of v1] (f3);
        \vertex[below left = of v2] (f4);
        \vertex[below right = of v2] (f5);
        \vertex[above right = of v2] (f6);
        \diagram* {
          (f1) -- (v1) -- (f3),
          (f2) -- (v1) --[scalar] (v2),
          (f4) -- (v2) -- (f5),
          (v2) -- (f6), };
      \end{feynman}
    \end{tikzpicture}}
  = -\alpha_3^{(2)} \sum_{\abs{\set{\mu,\nu,\rho}}=3}
  G^{rs}_{r's'} G^{s't}_{s''t'}
  \c_{\mu r'}^\dag \c_{\nu s''}^\dag \c_{\rho t'}^\dag
  \c_{\rho t} \c_{\nu s} \c_{\mu r},
  \label{eq:H_3_2}
\end{align}
where $\alpha_3^{(2)} \equiv \sum_{n>0} K_n^2/E_n$, and the preceding
minus sign is as prescribed by $H_{\t{int}}^{(2)}$ in
\eqref{eq:H_int_1_2}.

@@

which can be expanded and solved explicitly for the counter-terms to
find
  \widetilde G^{rs}_{r''s''}
  = \sum_{\ell,m,r',s'} \f{K_{\ell m}^2}{K E_{\ell m}}

@@

$\Lambda\to\infty$.  This procedure ensures that $\alpha_{3,2}^{(3)}$
always remains finite.

>>>>

Our theory of effective multi-body interactions assumes no
non-universal contribution to the three-body interaction energy, which
is to say that we assume the absence of real (as opposed to
effective), bare three-body interactions.  Consequently, three-body
interactions do not appear until second order in the coupling
constants of the effective theory, in the expansion of
$H_{\t{int}}^{(2)}$ in \eqref{eq:H_int_1_2}.  The virtual state of
three-body terms in $H_{\t{int}}^{(2)}$ cannot have two atoms in
excited motional states, as otherwise the second application of
$H_{\t{int}}$ in $H_{\t{int}}^{(2)}$ would have to address both of
theses atoms to bring them back down to the ground state, resulting in
a two-body process as in the second diagram of
\eqref{eq:H_2_expansion}.  All second-order three-body terms must
therefore have only one excited atom in the virtual state, and take
the form
\begin{align}
  \begin{tikzpicture}
    \begin{feynman}
      \vertex (v1);
      \vertex[above left = of v1] (f1) {$\mu r$};
      \vertex[below left = of v1] (f2) {$\nu s$};
      \vertex[right = of v1] (vm);
      \vertex[right = of vm] (v2);
      \vertex[above = of vm] (f3) {$\mu r'$};
      \vertex[below = of vm] (f4) {$\rho t$};
      \vertex[below right = of v2] (f5) {$\rho t'$};
      \vertex[above right = of v2] (f6) {$\nu s''$};
      \diagram* {
        (f1) -- (v1) -- (f3),
        (f2) -- (v1) --  [scalar, edge label=$n\nu s'$] (v2),
        (f4) -- (v2) -- (f5),
        (v2) -- (f6), };
    \end{feynman}
  \end{tikzpicture}
  \propto K_n^2 G^{rs}_{r's'} G^{s't}_{s''t'}
  \c_{\mu r'}^\dag \c_{\nu s''}^\dag \c_{\rho t'}^\dag
  \c_{\rho t} \c_{\nu s} \c_{\mu r}
  \label{eq:H_3_2_diagram}.
\end{align}
Unlike for the two-body diagram in \eqref{eq:H_2}, the explicit
factors of $1/2$ which appear in the bare two-body Hamiltonian
$H_{\t{int}}$ in \eqref{eq:H_int} are now cancelled out by symmetry
factors which account for duplicate diagrams; this cancellation will
generally occur for all connected $M$-body diagrams with $M>2$ (see
Appendix \ref{sec:diagrams}).  The net effective three-body
interaction Hamiltonian at second order is then given by the sum over
all diagrams of the form in \eqref{eq:H_3_2_diagram}, i.e.
\begin{align}
  H_3^{(2)} = - \shrink{
    \begin{tikzpicture}
      \begin{feynman}
        \vertex (v1);
        \vertex[above left = of v1] (f1);
        \vertex[below left = of v1] (f2);
        \vertex[right = 4em of v1] (v2);
        \vertex[above right = of v1] (f3);
        \vertex[below left = of v2] (f4);
        \vertex[below right = of v2] (f5);
        \vertex[above right = of v2] (f6);
        \diagram* {
          (f1) -- (v1) -- (f3),
          (f2) -- (v1) --[scalar] (v2),
          (f4) -- (v2) -- (f5),
          (v2) -- (f6), };
      \end{feynman}
    \end{tikzpicture}}
  = -\alpha_3^{(2)} \sum_{\abs{\set{\mu,\nu,\rho}}=3}
  G^{rs}_{r's'} G^{s't}_{s''t'}
  \c_{\mu r'}^\dag \c_{\nu s''}^\dag \c_{\rho t'}^\dag
  \c_{\rho t} \c_{\nu s} \c_{\mu r},
  \label{eq:H_3_2}
\end{align}
where $\alpha_3^{(2)} \equiv \sum_{n>0} K_n^2/E_n$, and the preceding
minus sign is as prescribed by $H_{\t{int}}^{(2)}$ in
\eqref{eq:H_int_1_2}.

@@

which can be expanded to find
  K \widetilde G^{rs}_{r''s''}
  = \sum_{\ell,m,r',s'} \f{K_{\ell m}^2}{E_{\ell m}}

@@

$\Lambda\to\infty$.  This procedure ensures that there are no
divergences in $\alpha_{3,2}^{(3)}$.
